Re-examining cross-cultural similarity judgments using language statistics

### 2023-02-02 code/4_paper/manuscript/manuscript.tex
final pdf

Our study uses cosine distances of fastText word vectors as a measure of
lexical co-occurrence.\footnote{With the preregistered exclusion
  criterion, all three corpora were significant predictors.} fastText is
a system that uses lexical co-occurrence information to generate a
vector representing each word in its lexicon (Mikolov, Grave,
Bojanowski, Puhrsch, \& Joulin, 2018). Practically speaking, fastText
vectors are available for many languages, and fastText has also been
shown to be sensitive to cultural differences in word meanings: Thompson
\& Lupyan (2020) demonstrated that the distribution of semantic meaning
clusters generated by fastText trained on language-specific corpora
correlates with the cultural, historical, and geographical similarities
of these languages.

@@

For US responding: only the English (EN) corpus was a significant
predictor{[}\^{}2{]}. EN corpus: \(\beta\) = -6.96, \(\chi^2\)(1) =
16.57, p \textless{} .001. VI corpus: \(\beta\) = -2.22, \(\chi^2\)(1) =
3.73, p = 0.054. ZH corpus: \(\beta\) = -3.18, \(\chi^2\)(1) = 3.37, p =
0.066.

>>>>

Our study uses cosine distances of fastText word vectors as a measure of
lexical co-occurrence.\footnote{We also carried out our analysis using
  raw lexical cooccurrences and obtained similar results.} fastText is a
system that uses lexical co-occurrence information to generate a vector
representing each word in its lexicon (Mikolov, Grave, Bojanowski,
Puhrsch, \& Joulin, 2018). Practically speaking, fastText vectors are
available for many languages, and fastText has also been shown to be
sensitive to cultural differences in word meanings: Thompson \& Lupyan
(2020) demonstrated that the distribution of semantic meaning clusters
generated by fastText trained on language-specific corpora correlates
with the cultural, historical, and geographical similarities of these
languages.

@@

For US responding: only the English (EN) corpus was a significant
predictor\footnote{With the preregistered exclusion criterion, only the
  English (EN) and Mandarin (ZH) corpus were significant predictors.}.
EN corpus: \(\beta\) = -6.96, \(\chi^2\)(1) = 16.57, p \textless{} .001.
VI corpus: \(\beta\) = -2.22, \(\chi^2\)(1) = 3.73, p = 0.054. ZH
corpus: \(\beta\) = -3.18, \(\chi^2\)(1) = 3.37, p = 0.066.
